Community context determines competition/facilitation trade-offs in pollination systems

### 2019-05-07 paper/manuscript.Rmd
Update keywords

loadd(abs_wordcount, msc_wordcount, n_displays, n_references)
```

@@

**Running title:** The pollination trade-off

**Keywords:** Competition, facilitation, interspecific pollen transfer, conspecific, pollen deposition, multi-species, plant-pollinator interaction, pollination trade-off, pollination costs, networks (up to 10).

>>>>

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
```

@@

**Keywords:** `r keywords`
